\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{fontawesome5}
% \usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}

% adjust the page margins
\usepackage[scale=0.9]{geometry}
% \setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{xcolor}

% personal data
\name{Linden}{Parkes, Ph.D.}
% \address{Postdoctoral Research Fellow, Department of Bioengineering}{311 Hayden Hall, University of Pennsylvania, Philadelphia, PA 19104}{}
\address{K99/R00 Postdoctoral Research Fellow, University of Pennsylvania}{}{}

\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcventryalt}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l}
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-15mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faIcon{globe} lindenparkes.com & \faIcon{envelope} lindenmp@seas.upenn.edu & \faIcon{github} \href{https://github.com/lindenmp}{lindenmp} & \faIcon{twitter} \href{https://twitter.com/LindenParkes}{LindenParkes}\\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%% Academic Positions %%%%%%%%%%%%%%%%
\section{Research Interests}
I am a \textbf{computational neuroscientist} seeking to uncover the pathways that track the emergence of psychopathology. I approach this goal from a neurobiological perspective by studying how complex neural systems shape behavior and cognition, and how dysfunction in these systems predicts psychopathology.
%%%%%%%%%%%%%%%% Academic Positions %%%%%%%%%%%%%%%%
\section{Academic Positions}

{\customcventry{July 2019 - present}{University of Pennsylvania, Department of Bioengineering}{Postdoctoral Research Fellow}{Philadelphia, PA}{}
{\begin{itemize}
  \item Advisors: Prof. Dani S. Bassett, Associate Prof. Theodore D. Satterthwaite
\end{itemize}
}

{\customcventry{Sept. 2018 - Oct. 2018}{Donders Institute for Brain, Cognition and Behaviour}{Visiting Scholar}{Nijmegen, The Netherlands}{}
{\begin{itemize}
  \item Advisors: Prof. Christian Beckmann, Dr. Andre Marquand
\end{itemize}
}

%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%
\section{Education}

{\customcventry{March 2014 - June 2019}{Monash University}{Doctor of Philosophy, Neuroscience \& Psychiatry}{Melbourne, Australia}{}
{\begin{itemize}
  \item Thesis: Mapping brain networks in health and mental disorder with structural and functional Magnetic Resonance Imaging
  \item Advisors: Prof. Murat Yucel, Prof. Alex Fornito, Dr. Ben Fulcher
\end{itemize}
}

{\customcventry{2009 - 2013}{Swinburne University of Technology}{Bachelor of Science (with Honors), Psychology/Psychophysiology}{Melbourne, Australia}{}
{\begin{itemize}
  \item Thesis: Mapping language processes using Magnetoencephalography.
  \item Advisor: Associate Prof. Conrad Perry
  \item Honors: First Class. Dux
\end{itemize}
}

%%%%%%%%%%%%%%%% Funding %%%%%%%%%%%%%%%%
% \section{Funding (pending)}
% \section{Funding (awarded)}
\section{Funding}
\subsection{Career Transition Awards}
{\customcventryalt{K99/R00 Pathway to Independence Award}{Sept. 2021 - 2026}{National Institute of Mental Health (NIMH)}
{\begin{itemize}
  \item Project: Developing prognostic neuroimaging biomarkers of the psychosis spectrum using network control theory
  \item \$1,424,194 USD
\end{itemize}
}

\subsection{Fellowships \& Scholarships}

{\customcventryalt{Young Investigator Award}{Jan. 2021 - Jan. 2023}{Brain \& Behavior Research Foundation}{}{}
{\begin{itemize}
  \item Project: Hybrid neurodevelopmental normative models for psychosis
  \item \$70,000 USD
\end{itemize}
}

{\customcventryalt{Monash University Postgraduade Publication Award}{2018}{Monash University}{}{}
{\begin{itemize}
  \item \$6,300 AUD
\end{itemize}
}

{\customcventryalt{Monash University Graduate Research Scholarship}{2014 - 2018}{Monash University}{}{}
{\begin{itemize}
  \item \$20,000 AUD
\end{itemize}
}

{\customcventryalt{Australian Postgraduate Award Research Scholarship}{2014 - 2018}{Australian Government}{}{}
{\begin{itemize}
  \item \$91,000 AUD
\end{itemize}
}

\subsection{Grants}
{\customcventryalt{Innovations Connections Grant}{2016 - 2017}{Department of Industry, Innovation and Science, Australia}{}{}
{\begin{itemize}
  \item \$50,000 AUD
  \item Associate investigator
\end{itemize}
}

% {\customcventryalt{Swartz Foundation}{2020 - 2021}{}{}{}
% {\begin{itemize}
%   \item \$75,000 USD
%   \item Associate investigator
% \end{itemize}
% }

\subsection{Travel Awards}
{\customcventryalt{Domestic Travel Fellowship Award}{2022}{Society of Biological Psychiatry}{}{}
{\begin{itemize}
  \item \$2,000 USD
\end{itemize}
}

{\customcventryalt{Abstract Merit Award}{2021}{Organization for Human Brain Mapping}{}{}
{\begin{itemize}
  \item virtual, no monetary component
\end{itemize}
}

{\customcventryalt{Abstract Merit Award}{2020}{Organization for Human Brain Mapping}{}{}
{\begin{itemize}
  \item \$3,000 USD
\end{itemize}
}

{\customcventryalt{Donders-Monash Erasmus Travel Award}{2018}{Donders Institute for Brain, Cognition and Behaviour | Monash University}{}{}
{\begin{itemize}
  \item \$3,200 AUD
\end{itemize}
}

{\customcventryalt{Future Leaders Travel Award}{2015}{Monash Institute of Cognitive and Clinical Neurosciences}{}{}
{\begin{itemize}
  \item \$5,000 AUD
\end{itemize}
}

%%%%%%%%%%%%%%%% Select Publications %%%%%%%%%%%%%%%%
\section{Publications}

\subsection{First author}
\cvitem{}{\textbf{Parkes L}, Kim JZ, Stiso J, Calkins ME, Cieslak M, Gur RE, Gur RC, Moore TM, Ouellet M, Roalf DR, Shinohara RT, Wolf DH, Satterthwaite TD, \& Bassett DS (2022). Asymmetric signaling across the hierarchy of cytoarchitecture within the human connectome. \href{https://www.biorxiv.org/content/10.1101/2022.05.13.491642v1.abstract}{\emph{\textcolor{blue}{bioRxiv}}}.}

\cvitem{}{\textbf{Parkes L}, Moore TM, Calkins ME, Cieslak M, Roalf DR, Wolf DH, Gur RC, Gur RE, Satterthwaite TD \& Bassett DS (2021). Network controllability in transmodal cortex predicts positive psychosis spectrum symptoms. \href{https://www.sciencedirect.com/science/article/pii/S0006322321011756}{\emph{\textcolor{blue}{Biological Psychiatry}}}, 90 (6), 409-418.}

\cvitem{}{\textbf{Parkes L}, Moore TM, Calkins ME, Cook PA, Cieslak M, Roalf DR, Wolf DH, Gur RC, Gur RE, Satterthwaite TD \& Bassett DS (2021). Transdiagnostic dimensions of psychopathology explain individuals' unique deviations from normative neurodevelopment in brain structure. \href{https://www.nature.com/articles/s41398-021-01342-6}{\emph{\textcolor{blue}{Translational Psychiatry}}}, 11 (1), 1-13.}

\cvitem{}{\textbf{Parkes L}, Satterthwaite TD \& Bassett DS (2020). Towards precise resting-state fMRI biomarkers in psychiatry: synthesizing developments in transdiagnostic research, dimensional models of psychopathology, and normative neurodevelopment. \href{https://www.sciencedirect.com/science/article/pii/S0959438820301616}{\emph{\textcolor{blue}{Current Opinion in Neurobiology}}}, 65, 120-128.}
{\begin{itemize}
  \item Invited opinion piece
\end{itemize}
}

\cvitem{}{\textbf{Parkes L}, Tiego J, Aquino K, Braganza L, Chamberlain SR, Fontenelle L, Harrison BJ, Lorenzetti V, Paton B, Razi A, Fornito A, \& Yucel M (2019). Transdiagnostic variations in impulsivity and compulsivity in obsessive-compulsive disorder and gambling disorder correlate with effective connectivity in cortical-striatal-thalamic-cortical circuits. \href{https://www.sciencedirect.com/science/article/pii/S1053811919306585}{\emph{\textcolor{blue}{NeuroImage}}}, 202, 116070.}

\cvitem{}{\textbf{Parkes L}, Fulcher B, Yucel M, \& Fornito A (2018). An evaluation of the efficacy, reliability, and sensitivity of motion correction strategies for resting-state functional MRI. \href{https://www.sciencedirect.com/science/article/pii/S1053811917310972}{\emph{\textcolor{blue}{NeuroImage}}}, 171, 415-436.}

\cvitem{}{*Prochazkova L, \textbf{*Parkes L}, Dawson A, Youssef G, Ferreira GM, Lorenzetti V, Segrave RA, Fontenelle LF, \& Yucel M (2018). Unpacking the role of self-reported compulsivity and impulsivity in obsessive-compulsive disorder. \href{https://www.cambridge.org/core/journals/cns-spectrums/article/abs/unpacking-the-role-of-selfreported-compulsivity-and-impulsivity-in-obsessivecompulsive-disorder/3AE081173C6A8931ACDB7E779630DAD0}{\emph{\textcolor{blue}{CNS spectrums}}}, 23 (1), 51-58.}
\textit{*These authors contributed equally}}

\cvitem{}{\textbf{Parkes L}, Fulcher B, Yucel M, \& Fornito A (2017). Transcriptional signatures of connectomic subregions of the human striatum. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/gbb.12386}{\emph{\textcolor{blue}{Genes, Brain and Behavior}}}, 16 (7), 647-663.}

\cvitem{}{\textbf{Parkes L}, Perry C, \& Goodin P (2016). Examining the N400m in affectively negative sentences. A magnetoencephalography study. \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/psyp.12601}{\emph{\textcolor{blue}{Psychophysiology}}}, 53 (5), 689-704.}

\subsection{Senior author}
\cvitem{}{Segrave RA, Hendrikse J, \& \textbf{Parkes L} (2019). DBS, TMS and tDCS for obsessive compulsive disorder. In \textit{A Transdiagnostic Approach to Obsessions, Compulsions and Related Phenomena}, 255-278. Cambridge University Press.}

\subsection{Consortium papers}
\cvitem{}{Richie-Halford A, Cieslak M, Ai L, Caffarra S, Covitz S, Franco AR, Karipidis II, Kruper J, Milham M, Avelar-Pereira B, Roy E, Sydnor VJ, Yeatman J, \textbf{Fibr Community Science Consortium}, Satterthwaite TD, \& Rokem A (2022). An open, analysis-ready, and quality controlled resource for pediatric brain white-matter research. \emph{bioRxiv}.}

\subsection{Middle author}
\cvitem{}{Gu S, Fotiadis P, \textbf{Parkes L}, \emph{et al.} (2022). Network controllability mediates the relationship between rigid structure and flexible dynamics. \emph{Network Neuroscience}, 6 (1), 275-297.}

\cvitem{}{Aquino KM, Fulcher B, Oldham S, \textbf{Parkes L}, \emph{et al.} (2022). On the intersection between data quality and dynamical modelling of large-scale fMRI signals. \emph{NeuroImage}, 256, 119051.}

\cvitem{}{Pines AR, Larsen B, Cui Z, Sydnor VJ, Bertolero MA, Adebimpe A, Alexander-Bloch AF, Davatzikos C, Fair DA, Gur RC, Gur RE, Li H, Milham MP, Moore TM, Murtha K, \textbf{Parkes L}, \emph{et al.} (2022). Dissociable multi-scale patterns of development in personalized brain networks. \emph{Nature communications}, 13 (1), 2647.}

\cvitem{}{Den Ouden L, Suo C, Albertella L, Greenwood L-M, Lee RSC, Fontenelle LF, \textbf{Parkes L}, \emph{et al.} (2022). Transdiagnostic phenotypes of compulsive behavior and associations with psychological, cognitive, and neurobiological affective processing. \emph{Translational psychiatry}, 12 (1), 1-11.}

\cvitem{}{Segal A, \textbf{Parkes L}, \emph{et al.} (2022). Regional, circuit, and network heterogeneity of brain abnormalities in psychiatric disorders. \emph{medRxiv}.}

\cvitem{}{Murtha K, Larsen B, Pines A, \textbf{Parkes L}, \emph{et al.} (2022). Associations between neighborhood socioeconomic status, parental education, and executive system activation in youth. \emph{Cerebral Cortex}.}

\cvitem{}{Srivastava P, Fotiadis P, \textbf{Parkes L}, \& Bassett DS (2022). The expanding horizons of network neuroscience: From description to prediction and control. \emph{NeuroImage}, 119250.}

\cvitem{}{Zhang X, Chye Y, Braganza L, Fontenelle LF, Harrison BJ, \textbf{Parkes L}, \emph{et al.} (2021). Severity related neuroanatomical alteration across symptom dimensions in obsessive-compulsive disorder. \emph{Journal of Affective Disorders Reports}, 4, 100129.}

\cvitem{}{Mahadevan AS, Cornblath EJ, Lydon-Staley DM, Zhou D, \textbf{Parkes L}, \emph{et al.} (2021). Alprazolam modulates persistence energy during emotion processing in first-degree relatives of individuals with schizophrenia: a network control study. \emph{bioRxiv}.}

\cvitem{}{McGowan AL, \textbf{Parkes L}, \emph{et al.} (2021). Controllability of structural brain networks and the waxing and waning of negative affect in daily life. \emph{Biological Psychiatry Global Open Science}.}

\cvitem{}{He X, Caciagli L, \textbf{Parkes L}, \emph{et al.} (2021). Pathological and metabolic underpinnings of energetic inefficiency in temporal lobe epilepsy. \emph{bioRxiv}.}

\cvitem{}{Zhou D, Kang Y, Cosme D, Jovanova M, He X, Mahadevan A, Stanoi O, Brynildsen JK, Cooper N, Cornblath E, \textbf{Parkes L}, \emph{et al.} (2021). Mindfulness promotes control of brain network dynamics for self-regulation and discontinues the past from the present. \emph{PsyArXiv}.}

\cvitem{}{Fallon J, Ward PGD, \textbf{Parkes L}, \emph{et al.} (2020). Timescales of spontaneous fMRI fluctuations relate to structural connectivity in the brain. \emph{Network Neuroscience}, 4 (3), 788-806.}

\cvitem{}{Aquino KM, Fulcher BD, \textbf{Parkes L}, \emph{et al.} (2020). Identifying and removing widespread signal deflections from fMRI data: Rethinking the global signal regression problem. \emph{NeuroImage}, 212, 116614.}

\cvitem{}{Maleki S, Chye Y, Zhang X, \textbf{Parkes L}, \emph{et al.} (2020). Neural correlates of symptom severity in obsessive-compulsive disorder using magnetization transfer and diffusion tensor imaging. \emph{Psychiatry Research: Neuroimaging}, 298, 111046.}

\cvitem{}{Amiet D, Youssef GJ, Hagg LJ, Lorenzetti V, \textbf{Parkes L}, \emph{et al.} (2020). Young adults with higher motives and expectancies of regular cannabis use show poorer psychosocial functioning. \emph{Frontiers in Psychiatry}, 1449.}

\cvitem{}{Oldham S, Fulcher B, \textbf{Parkes L}, \emph{et al.} (2019). Consistency and differences between centrality measures across distinct classes of networks. \emph{PloS one}, 14 (7), e0220061.}

\cvitem{}{Sabaroedin K, Tiego J, \textbf{Parkes L}, \emph{et al.} (2019). Functional connectivity of corticostriatal circuitry and psychosis-like experiences in the general community. \emph{Biological Psychiatry}, 86 (1), 16-24.}

\cvitem{}{Contreras-Rodriguez O, Burrows T, Pursey KM, Stanwell P, \textbf{Parkes L}, \emph{et al.} (2019). Food addiction linked to changes in ventral striatum functional connectivity between fasting and satiety. \emph{Appetite}, 133, 18-23.}

\cvitem{}{Tiego J, Oostermeijer S, Prochazkova L, \textbf{Parkes L}, \emph{et al.} (2019). Overlapping dimensional phenotypes of impulsivity and compulsivity explain co-occurrence of addictive and related behaviors. \emph{CNS spectrums}, 24 (4), 426-440.}

\cvitem{}{Jamadar SD, Ward PGD, Carey A, McIntyre R, \textbf{Parkes L}, \emph{et al.} (2019). Radiotracer administration for high temporal resolution positron emission tomography of the human brain: application to FDG-fPET. \emph{JoVE (Journal of Visualized Experiments)}, 152, e60259.}

\cvitem{}{Chamberlain SR, Tiego J, Fontenelle LF, Hook R, \textbf{Parkes L}, \emph{et al.} (2019). Fractionation of impulsive and compulsive trans-diagnostic phenotypes and their longitudinal associations. \emph{Australian \& New Zealand Journal of Psychiatry}, 53 (9), 896-907.}

\cvitem{}{Den Ouden L, Kandola A, Suo C, Hendrikse J, Costa RJS, Watt MJ, Lorenzetti V, Chye Y, \textbf{Parkes L}, \emph{et al.} (2018). The influence of aerobic exercise on hippocampal integrity and function: preliminary findings of a multi-modal imaging analysis. \emph{Brain Plasticity}, 4 (2), 211-216.}

\cvitem{}{Bennett D, Oldham S, Dawson A, \textbf{Parkes L}, \emph{et al.} (2017). Systematic overestimation of reflection impulsivity in the Information Sampling Task. \emph{Biological Psychiatry}, 82 (4), e29-e30.}

\cvitem{}{Yücel M, Carter A, Allen AR, Balleine B, Clark L, Dowling NA, Gainsbury SM, Goudriaan AE, Grant J, Hayes A, Hodgins D, van Holst R, Lattimore R, Livingstone C, Lorenzetti V, Lubman D, Murawski C, \textbf{Parkes L}, \emph{et al.} (2017). Neuroscience in gambling policy and treatment: an interdisciplinary perspective. \emph{The Lancet Psychiatry}, 4 (6), 501-506.}

\cvitem{}{Guo K, Youssef GJ, Dawson A, \textbf{Parkes L}, \emph{et al.} (2017). A psychometric validation study of the Impulsive-Compulsive Behaviours Checklist: A transdiagnostic tool for addictive and compulsive behaviours. \emph{Addictive behaviors}, 67, 26-33.}

\cvitem{}{Jung WH, Yücel M, Yun J-Y, Yoon YB, Cho KIK, \textbf{Parkes L}, \emph{et al.} (2017). Altered functional network architecture in orbitofronto‐striato‐thalamic circuit of unmedicated patients with obsessive‐compulsive disorder. \emph{Human Brain Mapping}, 38 (1), 109-119.}

\cvitem{}{}


% \cvitem{}{Gu S, Fotiadis P, \textbf{Parkes L}, Xia CH, Gur RC, Gur RE, Roalf DR, Satterthwaite TD, \& Bassett DS (2022). Network controllability mediates the relationship between rigid structure and flexible dynamics. \emph{Network Neuroscience}, 6 (1), 275-297.}
%
% \cvitem{}{Aquino KM, Fulcher B, Oldham S, \textbf{Parkes L}, Gollo L, Deco G, \& Fornito A (2022). On the intersection between data quality and dynamical modelling of large-scale fMRI signals. \emph{NeuroImage}, 256, 119051.}
%
% \cvitem{}{Pines AR, Larsen B, Cui Z, Sydnor VJ, Bertolero MA, Adebimpe A, Alexander-Bloch AF, Davatzikos C, Fair DA, Gur RC, Gur RE, Li H, Milham MP, Moore TM, Murtha K, \textbf{Parkes L}, Thompson-Schill SL, Shanmugan S, Shinohara RT, Weinstein SM, Bassett DS, Fan Y, \& Satterthwaite TD (2022). Dissociable multi-scale patterns of development in personalized brain networks. \emph{Nature communications}, 13 (1), 2647.}
%
% \cvitem{}{Den Ouden L, Suo C, Albertella L, Greenwood L-M, Lee RSC, Fontenelle LF, \textbf{Parkes L}, Tiego J, Chamberlain SR, Richardson K, Segrave R, \& Yücel M (2022). Transdiagnostic phenotypes of compulsive behavior and associations with psychological, cognitive, and neurobiological affective processing. \emph{Translational psychiatry}, 12 (1), 1-11.}
%
% \cvitem{}{Segal A, \textbf{Parkes L}, Aquino K, Kia SM, Wolfers T, Franke B, Hoogman M, Beckmann CF, Westlye LT, Andreassen OA, Zalesky A, Harrison BJ, Davey C, Soriano-Mas C, Cardoner N, Tiego J, Yücel M, Braganza L, Suo C, Berk M, Cotton S, Bellgrove MA, Marquand AF, \& Fornito A (2022). Regional, circuit, and network heterogeneity of brain abnormalities in psychiatric disorders. \emph{medRxiv}.}
%
% \cvitem{}{Murtha K, Larsen B, Pines A, \textbf{Parkes L}, Moore TM, Adebimpe A, Bertolero M, Alexander-Bloch A, Calkins ME, Davila DG, Lindquist MA, Mackey AP, Roalf DR, Scott JC, Wolf DH, Gur RC, Gur RE, Barzilay R, \& Satterthwaite TD (2022). Associations between neighborhood socioeconomic status, parental education, and executive system activation in youth. \emph{Cerebral Cortex}.}
%
% \cvitem{}{Srivastava P, Fotiadis P, \textbf{Parkes L}, \& Bassett DS (2022). The expanding horizons of network neuroscience: From description to prediction and control. \emph{NeuroImage}, 119250.}
%
% \cvitem{}{Zhang X, Chye Y, Braganza L, Fontenelle LF, Harrison BJ, \textbf{Parkes L}, Sabaroedin K, Maleki S, Yücel M, \& Suo C (2021). Severity related neuroanatomical alteration across symptom dimensions in obsessive-compulsive disorder. \emph{Journal of Affective Disorders Reports}, 4, 100129}
%
% \cvitem{}{Mahadevan AS, Cornblath EJ, Lydon-Staley DM, Zhou D, \textbf{Parkes L}, Larsen B, Adebimpe A, Kahn AE, Gur RC, Gur RE, Satterthwaite TD, Wolf DH, \& Bassett DS (2021). Alprazolam modulates persistence energy during emotion processing in first-degree relatives of individuals with schizophrenia: a network control study. \emph{bioRxiv}.}
%
% \cvitem{}{McGowan AL, \textbf{Parkes L}, He X, Stanoi O, Kang Y, Lomax S, Jovanova M, Mucha PJ, Ochsner KN, Falk EB, Bassett DS, \& Lydon-Staley DM (2021). Controllability of structural brain networks and the waxing and waning of negative affect in daily life. \emph{Biological Psychiatry Global Open Science}.}
%
% \cvitem{}{He X, Caciagli L, \textbf{Parkes L}, Stiso J, Karrer TM, Kim JZ, Lu Z, Menara T, Pasqualetti F, Sperling MR, Tracy JI, \& Bassett DS (2021). Pathological and metabolic underpinnings of energetic inefficiency in temporal lobe epilepsy. \emph{bioRxiv}.}
%
% \cvitem{}{Zhou D, Kang Y, Cosme D, Jovanova M, He X, Mahadevan A, Stanoi O, Brynildsen JK, Cooper N, Cornblath E, \textbf{Parkes L}, Mucha P, Ochsner KN, Lydon-Staley DM, Falk E, \& Bassett DS (2021). Mindfulness promotes control of brain network dynamics for self-regulation and discontinues the past from the present. \emph{PsyArXiv}.}
%
% \cvitem{}{Fallon J, Ward PGD, \textbf{Parkes L}, Oldham S, Arnatkevičiūtė A, Fornito A, \& Fulcher BD (2020). Timescales of spontaneous fMRI fluctuations relate to structural connectivity in the brain. \emph{Network Neuroscience}, 4 (3), 788-806.}
%
% \cvitem{}{Aquino KM, Fulcher BD, \textbf{Parkes L}, Sabaroedin K, \& Fornito A (2020). Identifying and removing widespread signal deflections from fMRI data: Rethinking the global signal regression problem. \emph{NeuroImage}, 212, 116614.}
%
% \cvitem{}{Maleki S, Chye Y, Zhang X, \textbf{Parkes L}, Chamberlain SR, Fontenelle LF, Braganza L, Youssef G, Lorenzetti V, Harrison BJ, Yücel M, \& Suo C (2020). Neural correlates of symptom severity in obsessive-compulsive disorder using magnetization transfer and diffusion tensor imaging. \emph{Psychiatry Research: Neuroimaging}, 298, 111046.}
%
% \cvitem{}{Amiet D, Youssef GJ, Hagg LJ, Lorenzetti V, \textbf{Parkes L}, Solowij N, \& Yücel M (2020). Young adults with higher motives and expectancies of regular cannabis use show poorer psychosocial functioning. \emph{Frontiers in Psychiatry}, 1449.}
%
% \cvitem{}{Oldham S, Fulcher B, \textbf{Parkes L}, Arnatkevičiūtė A, Suo C, \& Fornito A (2019). Consistency and differences between centrality measures across distinct classes of networks. \emph{PloS one}, 14 (7), e0220061.}
%
% \cvitem{}{Sabaroedin K, Tiego J, \textbf{Parkes L}, Sforazzini F, Finlay A, Johnson B, Pinar A, Cropley V, Harrison BJ, Zalesky A, Pantelis C, Bellgrove M, \& Fornito A (2019). Functional connectivity of corticostriatal circuitry and psychosis-like experiences in the general community. \emph{Biological Psychiatry}, 86 (1), 16-24.}

%%%%%%%%%%%%%%%% Teaching Experience %%%%%%%%%%%%%%%%
\section{Teaching Experience}
{\customcventry{2020}{University of Pennsylvania, Department of Bioengineering}{Teacher's Assistant}{Philadelphia, PA}{}
{\begin{itemize}
  \item Class: Network Neuroscience
  \item Course evaluation score: 3.57/4
\end{itemize}
}

{\customcventry{2019}{University of Pennsylvania, Department of Bioengineering}{Guest Lecturer}{Philadelphia, PA}{}
{\begin{itemize}
  \item Class: Network Neuroscience
\end{itemize}
}

{\customcventry{2017 - 2018}{Monash University}{Guest Lecturer}{Melbourne, Australia}{}
{\begin{itemize}
  \item Class: Neuroscience Methods
\end{itemize}
}

{\customcventry{2014 - 2015}{Swinburne University}{Recitation Tutor}{Melbourne, Australia}{}
{\begin{itemize}
  \item Class: Undergraduate Psychology
\end{itemize}
}

{\customcventry{2013}{Swinburne University}{Recitation Tutor}{Melbourne, Australia}{}
{\begin{itemize}
  \item Class: Undergraduate Physiology
\end{itemize}
}

%%%%%%%%%%%%%%%% Research Employment %%%%%%%%%%%%%%%%
\section{Research Employment}

{\customcventry{2018}{Monash Biomedical Imaging}{Research Assisstant}{Melbourne, Australia}{}
{\begin{itemize}
  \item Analysis of positron emission tomography (PET) data
\end{itemize}
}

{\customcventry{2016 - 2017}{Torus Games \& Cogstate}{Research Engineer}{Melbourne, Australia}{}
{\begin{itemize}
  \item Developed gamified cognitive tests for neuroscience research
\end{itemize}
}

{\customcventry{2013}{Swinburne Univerisity}{Magnetoencephalography Technician}{Melbourne, Australia}{}
{\begin{itemize}
  \item Collection, preprocessing, and analysis of Magnetoencephalography (MEG) data
\end{itemize}
}

%%%%%%%%%%%%%%%% Open Science Contributions %%%%%%%%%%%%%%%%
\section{Open Science Contributions}
\subsection{Toolkits}
{\customcventryalt{Network Control}{\faIcon{python} Python}{\url{https://github.com/BassettLab/control_package}}}
% {\customcventryalt{Predictive Clinical Neuroscience}{\faIcon{python} Python}{\url{https://github.com/amarquand/PCNtoolkit}}}

\subsection{Reproducibility}
{\customcventryalt{\url{https://github.com/lindenmp/neurodev_cs_predictive}}{\faIcon{python} Python}{}}
{\begin{itemize}
  \item Code to reproduce results presented in \href{https://www.sciencedirect.com/science/article/pii/S0006322321011756}{\emph{\textcolor{blue}{Parkes et al. (2021) Biological Psychiatry}}}
\end{itemize}
}

{\customcventryalt{\url{https://github.com/lindenmp/normative_neurodev_cs_t1}}{\faIcon{python} Python}{}}
{\begin{itemize}
  \item Code to reproduce results presented in \href{https://www.nature.com/articles/s41398-021-01342-6}{\emph{\textcolor{blue}{Parkes et al. (2021) Translational Psychiatry}}}
\end{itemize}
}

{\customcventryalt{\url{https://github.com/lindenmp/rs-fMRI}}{\faIcon{code} Matlab}{}}
{\begin{itemize}
  \item Code to reproduce results presented in \href{https://www.sciencedirect.com/science/article/pii/S1053811917310972}{\emph{\textcolor{blue}{Parkes et al. (2018) NeuroImage}} and \href{https://www.sciencedirect.com/science/article/pii/S1053811919306585}{\emph{\textcolor{blue}{Parkes et al. (2019) NeuroImage}}} }
\end{itemize}
}

%%%%%%%%%%%%%%%% Awards %%%%%%%%%%%%%%%%
% \section{Awards}

%%%%%%%%%%%%%%%% Presentations %%%%%%%%%%%%%%%%
\section{Presentations}
\subsection{Invited Lectures \& Presentations}

{\customcventryalt{Association for Psychological Science, Chicago, IL}{May 2022}{—Available on \href{https://youtu.be/oorEVqyTUio}{\textcolor{blue}{YouTube}}}
{\customcventryalt{Feindel Virtual Brain and Mind Lecture Series, McGill University, Canada}{May 2022}{}
{\customcventryalt{Mount Sinai, New York City, NY}{Mar. 2022}{}
{\customcventryalt{Vanderbilt University, Nashville, TN}{Mar. 2022}{}
{\customcventryalt{Rutgers University, New Brunswick, NJ}{Mar. 2022}{}
{\customcventryalt{University of Manchester, Manchester, United Kingdom}{Feb. 2022}{}
{\customcventryalt{The Douglas Research Centre, Montreal, Canada}{Feb. 2022}{}
{\customcventryalt{University of California, Los Angeles, CA}{Feb. 2022}{}
{\customcventryalt{Georgia State University, Atlanta, GA}{Nov. 2021}{}
{\customcventryalt{University of Pittsburgh, Pittsburgh, PA}{Oct. 2021}{—Available on \href{https://youtu.be/bo2AFvJ5mYU}{\textcolor{blue}{YouTube}}}
{\customcventryalt{Organization for Human Brain Mapping, Oral Presentation}{Jun. 2021}{}
{\customcventryalt{DataPhilly, Philadelphia, PA}{Mar. 2021}{—Available on \href{https://youtu.be/VdR5KmZ3OIU}{\textcolor{blue}{YouTube}}}
{\customcventryalt{Organization for Human Brain Mapping, Symposium}{Jun. 2020}{}
{\customcventryalt{Organization for Human Brain Mapping, Oral Presentation}{Jun. 2020}{}
{\customcventryalt{University of Pennsylvania, Philadelphia, PA}{Sep. 2018}{}
{\customcventryalt{Centre of Excellence for Integrative Brain Function, Melbourne, Australia}{Mar. 2018}{}
{\customcventryalt{Swinburne Univerisity, Melbourne, Australia}{Jun. 2016}{}
{\customcventryalt{Students of Brain Research, Melbourne, Australia}{Jun. 2015}{}
{\customcventryalt{Australasian Cognitive Neuroscience Conference, Melbourne, Australia}{Jun. 2013}{}

\subsection{Posters (first-author)}
{\customcventryalt{Network controllability in transmodal cortex predicts positive psychosis spectrum symptoms}{2021}{Organization for Human Brain Mapping}}
{\customcventryalt{Network controllability in transmodal cortex predicts positive psychosis spectrum symptoms}{2021}{Society of Biological Psychiatry}}
{\customcventryalt{Psychopathology explain individual’s unique deviations from normative neurodevelopment}{2020}{Organization for Human Brain Mapping}
{\customcventryalt{Impulsivity and compulsivity correlate with effective connectivity in corticostriatal circuits}{2019}{Organization for Human Brain Mapping}}
{\customcventryalt{Impulsivity and compulsivity correlate with effective connectivity in corticostriatal circuits}{2018}{Australasian Cognitive Neuroscience Conference}}
{\customcventryalt{Evaluating the efficacy and sensitivity of motion correction strategies for rs-fMRI}{2018}{Organization for Human Brain Mapping}}
{\customcventryalt{Efficacy, reliability, and sensitivity of motion correction strategies for resting-state functional MRI}{2017}{IEEE International Symposium on Biomedical Imaging}}
{\customcventryalt{Efficacy, reliability, and sensitivity of motion correction strategies for resting-state functional MRI}{2017}{Students of Brain Research}}

%%%%%%%%%%%%%%%% Academic Service %%%%%%%%%%%%%%%%
\section{Academic Service}
\subsection{Journal Peer Review}
{\begin{itemize}
  \item PNAS, Science Advances, Nature Protocols, NeuroImage, Human Brain Mapping, Network Neuroscience, Scientific Reports, Biological Psychiatry, Psychological Medicine, Neuropsychologia, Developmental Cognitive Neuroscience, NeuroImage: Clinical, Psychiatry Research: Neuroimaging, Harvard Review of Psychiatry, International Gambling Studies, Journal of Cerebral Blood Flow \& Metabolism
\end{itemize}
}

\subsection{Committees}

{\customcventryalt{Organization for Human Brain Mapping, Open Science Special Interest Group}{2022 - 2023}{Treasurer}}
{\customcventryalt{Organization for Human Brain Mapping, Student and Postdoc Special Interest Group}{2019 - 2021}{Treasurer}}
{\customcventryalt{Australasian Cognitive Neuroscience Society, Early Career Researchers Committee}{2017}{Committee Member}}
{\customcventryalt{Australasian Cognitive Neuroscience Society, Executive Committee}{2017}{ECR Representative}}
{\customcventryalt{Students of Brain Research}{2016}{Treasurer}}

\subsection{Supervision \& Mentorship}
{\customcventryalt{Ashlea Segal}{2018 - present}{Graduate Student, Monash University}}
{\customcventryalt{Tayla Currie}{2018}{Undergraduate Honors Student, Monash University}}
{\customcventryalt{John Fallon}{2017}{Undergraduate Honors Student, Monash University}}
{\customcventryalt{Luisa Prochazkova}{2016}{International Visiting Scholar, Monash University}}
{\customcventryalt{Kristina Sabaroedin}{2016}{Undergraduate Honors Student, Monash University}}
{\customcventryalt{Lauren Den Ouden}{2016}{Undergraduate Honors Student, Monash University}}
{\customcventryalt{Stuart Oldham}{2016}{Undergraduate Honors Student, Monash University}}
{\customcventryalt{Danielle Amiet}{2016}{Undergraduate Honors Student, Monash University}}

\subsection{Outreach \& Community Engagement}
{\customcventryalt{Neuroimaging Best Practices Beyond Open Science}{2021}{Organization for Human Brain Mapping, Student and Postdoc Special Interest Group}}
{\begin{itemize}
  \item Moderator
\end{itemize}
}

{\customcventryalt{Link with Mentors}{2021}{Organization for Human Brain Mapping, Student and Postdoc Special Interest Group}}
{\begin{itemize}
  \item Moderator
\end{itemize}
}

{\customcventryalt{International Mentoring Programme}{2021}{Organization for Human Brain Mapping, Student and Postdoc Special Interest Group}}
{\begin{itemize}
  \item Mentor
\end{itemize}
}

{\customcventryalt{Network Control Theory for Neuroscientists, Education Workshop}{2020}{Organization for Human Brain Mapping}}
{\begin{itemize}
  \item Organizer, presenter
\end{itemize}
}

{\customcventryalt{Link with Mentors}{2020}{Organization for Human Brain Mapping, Student and Postdoc Special Interest Group}}
{\begin{itemize}
  \item Moderator
\end{itemize}
}

{\customcventryalt{NeuroDay}{2018}{Methodist Ladies' College, Melbourne, Australia}}
{\begin{itemize}
  \item Organizer, presenter
\end{itemize}
}

{\customcventryalt{BMH Mentor Forum}{2018}{Brain \& Mental Health Research Hub, Monash University}}
{\begin{itemize}
  \item Organizer, mentor
\end{itemize}
}
{\customcventryalt{MBI Student Forum}{2014 - 2015}{Monash Biomedical Imaging, Monash University}}
{\begin{itemize}
  \item Organizer, mentor, presenter
\end{itemize}
}

\end{document}
